Weather Data Integration and Assimilation System\\

### 2020-02-10 method/sec_3-microservice.tex
Dont' use title case of figure captions. Capitalize only the proper nouns. Also, WDIAS can be shorten in figure captions.
Rearrange microservice doc

The microservice architectural style is an approach to developing a single application as a suite of small services, each running in its own process and communicating with lightweight mechanisms, often an HTTP resource API. These services are built around business capabilities and independently deployable by fully automated deployment machinery. There is a bare minimum of centralized management of these services, which may be written in different programming languages and use different data storage technologies. https://martinfowler.com/articles/microservices.html

Among the characteristics of \acrfull{microservice}, few characteristics heavily affect while moving from \acrshort{soa} to \acrshort{microservice}.
- Smart endpoints and dumb pipes \cite{LewisMicroservicesPipes}

- Pattern: Database per service \cite{LewisMicroservicesManagement}

@@

  \cite{RichardsonMicroservicesService}
  Keep each microservice’s persistent data private to that service and accessible only via its API. 
There are a few different ways to keep a service’s persistent data private. You do not need to provision a database server for each service. For example, if you are using a relational database then the options are:
Private-tables-per-service – each service owns a set of tables that must only be accessed by that service
Schema-per-service – each service has a database schema that’s private to that service
Database-server-per-service – each service has its own database server.
Private-tables-per-service and schema-per-service have the lowest overhead. Using a schema per service is appealing since it makes ownership clearer. Some high throughput services might need their own database server.

- Pattern: Sagas \cite{RichardsonMicroservicesSagas}
  In order to ensure loose coupling, each service has its own database. Maintaining data consistency between services is a challenge because 2 phase-commit/distributed transactions is not an option for many applications. An application must instead use the Saga pattern. A service publishes an event when its data changes. Other services consume that event and update their data.

Even AKKA.io actor model support the microservice architecture, as it explained in the documentation \cite{Akka.ioWhenCluster}, it has own advantages and disadvantage over the system that needs to be built.

- The Scale cube
The microservice architecture is an application of Y-axis scaling but let’s also look at X-axis and Z-axis scaling.

X-axis scaling
X-axis scaling consists of running multiple copies of an application behind a load balancer. If there are N copies then each copy handles 1/N of the load. This is a simple, commonly used approach of scaling an application.
One drawback of this approach is that because each copy potentially accesses all of the data, caches require more memory to be effective. Another problem with this approach is that it does not tackle the problems of increasing development and application complexity.

Y-axis scaling
Unlike X-axis and Z-axis, which consist of running multiple, identical copies of the application, Y-axis axis scaling splits the application into multiple, different services. Each service is responsible for one or more closely related functions. There are a couple of different ways of decomposing the application into services.
verb-based decomposition ex: checkout
decompose the application by noun ex: customer management. 
An application might use a combination of verb-based and noun-based decomposition.

Z-axis scaling
When using Z-axis scaling each server runs an identical copy of the code (similar to X-axis scaling). The big difference is that each server is responsible for only a subset of the data.

@@

- Brief introduction to the Kubernetes

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_async-v3.jpg}
    \caption{\acrshort{wdias} architecture to handle request asynchronously.}
    \label{fi:wdias_micro_async}
\end{figure}

\dbc{Dont' use title case of figure captions. Capitalize only the proper nouns. Also, WDIAS can be shorten in figure captions.}

>>>>

The microservice architectural style is an approach to developing a single application as a suite of small services, each running in its own process and communicating with lightweight mechanisms, often an HTTP resource API. These services are built around business capabilities and independently deployable by fully automated deployment machinery. There is a bare minimum of centralized management of these services, which may be written in different programming languages and use different data storage technologies \cite{LewisMicroservices}.

Among the characteristics of \acrfull{microservice}, few characteristics heavily affect while moving from \acrshort{soa} to \acrshort{microservice}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Smart Endpoints And Dumb Pipes}
\label{subse:smart_endpoints}
- Smart endpoints and dumb pipes \cite{LewisMicroservicesPipes}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Database per Service}
\label{subse:database_per_service}
- Pattern: Database per service \cite{LewisMicroservicesManagement}

@@

  \cite{RichardsonMicroservicesService}
  Keep each microservice’s persistent data private to that service and accessible only via its API. 
There are a few different ways to keep a service’s persistent data private. You do not need to provision a database server for each service. For example, if you are using a relational database then the options are:
\begin{itemize}
    \item Private-tables-per-service – each service owns a set of tables that must only be accessed by that service
    \item Schema-per-service – each service has a database schema that’s private to that service
    \item Database-server-per-service – each service has its own database server.
    \item Private-tables-per-service and schema-per-service have the lowest overhead. Using a schema per service is appealing since it makes ownership clearer. Some high throughput services might need their own database server.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Sagas}
\label{subse:sagas}
- Pattern: Sagas \cite{RichardsonMicroservicesSagas}
  In order to ensure loose coupling, each service has its own database. Maintaining data consistency between services is a challenge because 2 phase-commit/distributed transactions is not an option for many applications. An application must instead use the Saga pattern. A service publishes an event when its data changes. Other services consume that event and update their data.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The Scale Cube}
\label{subse:scale_cube}
The microservice architecture is an application of Y-axis scaling but let’s also look at X-axis and Z-axis scaling.

\subsubsection{X-axis Saling}
X-axis scaling consists of running multiple copies of an application behind a load balancer. If there are N copies then each copy handles 1/N of the load. This is a simple, commonly used approach of scaling an application.
One drawback of this approach is that because each copy potentially accesses all of the data, caches require more memory to be effective. Another problem with this approach is that it does not tackle the problems of increasing development and application complexity.

\subsubsection{Y-axis Scaling}
Unlike X-axis and Z-axis, which consist of running multiple, identical copies of the application, Y-axis axis scaling splits the application into multiple, different services. Each service is responsible for one or more closely related functions. There are a couple of different ways of decomposing the application into services.
verb-based decomposition ex: checkout
decompose the application by noun ex: customer management. 
An application might use a combination of verb-based and noun-based decomposition.

\subsubsection{Z-axis Scaling}
When using Z-axis scaling each server runs an identical copy of the code (similar to X-axis scaling). The big difference is that each server is responsible for only a subset of the data.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Brief introduction to the \acrfull{k8s}}
\label{sebse:k8s_intro}

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/k8s_architecture_v3.jpg}
    \caption{\acrfull{k8s} architecture.}
    \label{fi:k8s_architecture}
\end{figure}
